### 2017-03-15 ResearchNotes/data.tex
Correction in notes

After a first analysis of the data, the objects in the data are identified.
These objects are the courses, students, results, etc. Data mining tasks are
applied over these objects which are described by their features.

@@

A course also has a regime, a semester, a season, and a type. These features
are enumerated types because they have a limited domain. For example, the
semester may either be ``\textit{Par}'' or ``\textit{Ímpar}'' (Even or Odd),
the season may be ``\textit{Normal}'' or ``\textit{Special}''.

@@

Some courses have no Moodle. They are therefore useless for our these
experiments.

@@

The values for the \textit{StudentType} field are:

\begin{itemize}
    \item \textit{Normal}
    \item \textit{Interno}
\end{itemize}

Professors have only the features listed in table~\ref{tab:professor_features}.
The data contains a field called \textit{Role} which states if that Moodle user
is a professor or a student. Supposedly, if the user is a professor the role
has a value of 5. If it is a student, it has a value of 3. However, we see
entries for professors with a role value of 3 and vice versa. It is unknown if
this role actually state the if a user is a professor or student or something
else.

@@

\TODO{Talk about the profile dataset}

>>>>

After a first analysis of the data, the objects are identified.  These objects
are the courses, students, results, etc. Data mining tasks are applied over
these objects which are described by their features.

@@

A course also has a regime, a semester, a season, and a type. These features
are enumerated types because they have a limited domain. For example, the
semester may either be ``\textit{Par}'' or ``\textit{Ímpar}'' (Even or Odd),
the season may be ``\textit{Normal}'' or ``\textit{Especial}'' (Normal or
Special).

@@

Some courses have no Moodle. They are therefore useless for these experiments.

@@

The values for the \textit{StudentType} field are \textit{Normal} or
\textit{Interno} (Normal or Internal).

Professors have only the features listed in table~\ref{tab:professor_features}.
The data contains a field called \textit{Role} which states if that Moodle user
is a professor or a student. If the user is a professor the role has a value of
5. If it is a student, it has a value of 3. A few users with a value of 4 are
present. These users have the role of editor, but the Moodle logs only have 11
entries for a user of this role, so they are simply discarded.

@@

The \texttt{Profile} dataset contains the following calculated fields:

\begin{itemize}
    \item \texttt{NumberOfResources}
    \item \texttt{NumberOfActivities}
    \item \texttt{NumberOfViews}
    \item \texttt{NumberOfSubmissions}
\end{itemize}

### 2017-03-15 ResearchNotes/introduction.tex
Correction in notes

The objective of this project is to mine Moodle's data to find if user
activities explains their success. The hypothesis is that some behaviours in
courses during a semester may lead to success or lack there off.

This document contains the research notes made during the development of this
project. It contains a section on background, which has comments done to
papers, a listing of relevant journals and books, and some state of the art
regarding Data Mining, Educational Data Mining, and Moodle Mining.

The document also contains a section dedicate to the data which is used in this
project and a section detailing statistical analysis and experiments done to
that data.

>>>>

This document contains the research notes made during the development of the
thesis called ``Educational Data Mining applied to Moodle data from the
University of Évora''.

Initially, there are a few comments made to papers and books. Some journals are
also mentioned.

The document has a detailed explanation about the original data and how it was
processed into a data repository for experiments.

Information about statistics, processed datasets, and experiments are in their
own section.

Note that this document doesn't have all the information for the thesis. Some
text in the thesis was copy-pasted from this initial document, but a lot of
details are only added or corrected in the thesis text.
